Workflow and Software Documentation

### 2013-07-13 Workflow.Rnw
Explanation of changing the order of countries on a graph.

<<setup, include=FALSE>>=
require(knitr)
opts_chunk$set(
  tidy=FALSE
)
@

@@

<<>>=
standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q", 
                                         countryAbbrevsOrder=c("US", "UK", "JP", "CN", 
                                                               "ZA", "TZ", "SA", "IR", "ZM")), 
                     aes(a_0, c_t) ) +
  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
@

>>>>

<<setup, include=FALSE>>=
require(knitr)
opts_chunk$set(
  tidy=FALSE
)
source("Econ-Growth-Functions2.R")
@

@@

You can change the order of the countries on the graph 
with the \texttt{countryAbbrevsOrder} argument 
to \texttt{loadAllResampleData}. 
The default order is 
<<>>=
countryAbbrevs
@
However, for the 9-panel graphs, 
I like to plot in the order shown below, 
so that the SA/IR and TZ/ZM pairs 
are adjacent and atop one another, respectively.
The variable 
<<>>=
countryAbbrevsForGraph
@
\noindent in file \texttt{Econ-Growth-Functions2.R} contains the preferred
order for 9-panel graphs, as demonstrated below.
<<>>=
standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q", 
                                         countryAbbrevsOrder=countryAbbrevsForGraph), 
                     aes(a_0, c_t) ) +
  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
@
